### 2020-04-11 thesis_template/2_RelatedWork/model/spark.tex
documented rust memory management

\subsection{Move}
In Rust, for most types. operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
To understand how this assignment implementation is unique from other programing languages, Python, C++, and Rust code example of assigning list or vector of strings are shown in Figure. 
For example, a value is instantiated in a function. 
When it is returned to a new variable, the ownership of value is moved to the new variable. In Rust, one do not have to explicitly deallocate memory, 
because ownership of value is passed among variables across scope using move and eventually goes out of scope deallocating memory of the value.

>>>>

\subsection{Move}
In Rust, for most types operations like assigning a value to a variable, passing it to a function, or returning it from a function do not copy the value: they move it. 
With move, a value can be transferred from one owner to another. The previous variable does not have ownership of the value; it is moved to a newly assigned variable. 
To understand how this assignment implementation is unique from other programing languages, Java, C++, and Rust code example of assigning list or vector of strings are shown.

Below a few lines of code are initialization of list of string and reassigning it to other variables. 
\begin{lstlisting}
    List<String >s = new ArrayList<>(
                     Arrays.asList("lemon", "orange", "apple"))
    String t = s
    String u = s
 \end{lstlisting}
Figure~\ref{fig:pythonlist} represents the memory allocated after a Java ArrayList of strings is initialized and assigned to variable called s. After assigning s to t and to u, 
the memory representation become Figure~\ref{fig:pythonlistcopied}. The assignments are simply setting pointers to the ArrayList object and increment reference count.

\begin{figure}[htb]
    \includegraphics[width=10cm]{python_list_copied.eps}
    \caption{Representation of Java ArrayList of String}
    \label{fig:pythonlist}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=10cm]{python_list.eps}
    \caption{Representation of Java ArrayList of String after assignment to another variable}
    \label{fig:pythonlistcopied}
\end{figure}

Now, the analogous C++ code is shown below. 
\begin{lstlisting}
    vector<string> s = {"lemon", "orange", "apple"};
    vector<string> t = s;
    vector<string> u = s;
 \end{lstlisting}
Figure~\ref{fig:cpluscplusvector} shows the memory allocated when the vector is initialized. Figure~\ref{fig:cpluscplusvectorcopied} is a representation of after the assignments of s to t and to u. 
In C++, assigning value of vector to other variables involves allocating memory for new vector and copying the contents of the original vector to newly allocated one.

\begin{figure}[htb]
    \includegraphics[width=15cm]{cplusplus_vector.eps}
    \caption{Representation of C++ vector of string}
    \label{fig:cpluscplusvector}
\end{figure}

\begin{figure}[htb]
    \includegraphics[width=15cm]{cplusplus_vector_copied.eps}
    \caption{Representation of C++ vector of string after assignment to another variable}
    \label{fig:cpluscplusvectorcopied}
\end{figure}

In Rust code, the code is like below, 
\begin{lstlisting}
    let s = vec!["lemon".to_string, "orange".to_string, "apple".to_string];
    let t = s;
    let u = s;
 \end{lstlisting}

The representation of the original Vec of String in Rust is the almost same in C++ vector of string. Figure~\ref{fig:rustvecmoved} however shows different behavior when Rust assigns s to t. 
The value is moved to t from s so that the source variable s is uninitialized. The Rust code actually throws compile error, because we are assigning uninitialized variable at the last line.

\begin{figure}[htb]
    \includegraphics[width=15cm]{rust_vec_moved.eps}
    \caption{Representation of Rust Vec$<$String$>$ after assignment to another variable}
    \label{fig:rustvecmoved}
\end{figure}
